---
title: "What the Package Does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the Package Does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753CORBIN24)
```

# Introduction

This package was created by Connor Corbin for the class MATH-4753 at the University of Oklahoma. This package contains a multitude of different functions that were utilized throughout the class in lab assignments. The data set fire.R in the package is one of many data sets that I used in the class. This is also the data set that I studied and analyzed in my project report. 

# fire.r
fire data set which contains 15 entries comparing the distance in miles of a fire from the nearest fire station and the damage in thousands of dollars caused by the fire
```{r}
head(fire)
```


# ntickets.R function
This function calculates the number of tickets a airline should sell based on the probability of passengers actually showing up for their flight, the number of seats on the plane, and the desired likelihood of overbooking. 
```{r}
ntickets(N=200, gamma=0.01, p=0.95)
```


# myhypersim.R function
This function runs iter number of iterations where there are N total marbles, r white marbles, and n marbles drawn. The bar graph produced showcases the probability of different success numbers based off the results of the simulation
```{r}
myhyper(iter=100, N=15, r=8, n=5)
```

# scatterhist.R
This function creates a histogram and scatter plot side by side allowing for comparison of the two. 
```{r}
scatterhist(fire$DISTANCE, fire$DAMAGE, xlab="Distance", ylab="Damage")
```

# myncurve.R
This function calculates the probabilty of a function that is contained between a and -inf
```{r}
myncurve(5, 4, 2)
```

